---
title: "Ensemble time series - overview"
author: "Jean-Michel Perraud"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Ensemble time series - overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Time series libraries - overview
=================

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"', fig.align="center", fig.width=10, fig.height=8, dev='png')
```

```{r, eval=FALSE, include=FALSE}
library(swiftdev)
thisPkgDir <- file.path(find_uchronia_src_path(), 'bindings/R/pkgs/uchronia')
if(file.exists(thisPkgDir))
{
  setwd(file.path(thisPkgDir, 'vignettes'))
  purlVignettes('.','..')
}
```

# About this document

This document was generated from an R markdown file on `r as.character(Sys.time())`.

# Purpose

`uchronia` is a package to handle time series of varying geometry and dimensionality, using a C++ library for efficient handling "under the hood", but with conversion to `xts` time series in R when suitable. `uchronia` R package also has sibling in Python and MATLAB.

PLACEHOLDER TODO a vignette that does not rely on loading data but creating/manipulating live in-memory data.

