---
title: "Ensemble time series - overview"
author: "Jean-Michel Perraud"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Ensemble time series - overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Time series libraries - overview
=================

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"', fig.align="center", fig.width=10, fig.height=8, dev='png')
```

```{r, eval=FALSE, include=FALSE}
library(swiftdev)
thisPkgDir <- file.path(find_uchronia_src_path(), 'bindings/R/pkgs/uchronia')
if(file.exists(thisPkgDir))
{
  setwd(file.path(thisPkgDir, 'vignettes'))
  purlVignettes('.','..')
}
```

# About this document

This document was generated from an R markdown file on `r as.character(Sys.time())`.

# Elaboration

```{r, eval=FALSE, include=FALSE}
# if we want to debug, reminder possibly:
swiftr_dev() 
swiftr_dev(prepend_rlibpath_with='c:/RLibDev') 
```


```{r}
library(uchronia)
```

`uchronia` includes facilities to access time series from a "library", akin to what you would do to manage books. One way to describe such a library is to load a text description file written in the YAML format.

```{r}
# docDataPath <- Sys.getenv('SWIFT_SAMPLE_DATA_DIR') # swift::sampleDataDir()
sampleDataDir <- 'C:/STSF/sample/documentation'
dataLibraryFile <- file.path(sampleDataDir, 'time_series_library.yaml')
stopifnot(file.exists(dataLibraryFile))
```

Time series libraries are meant to hide the details of storage. Data is referenced by unique identifier, as a cornerstone for provenance management.

```{r}
dataLibrary <- getEnsembleDataSet(dataLibraryFile, '')
dataIds <- getDataSetIds(dataLibrary)
print(dataIds)
```

the function `getDataSet` will retrieve a reference to the data irrespective of its dimensionality. What we obtain is a "pointer" to data, not necessarily all the data which can be several gigabytes. 
Small enough data subsets can be converted to the popular `xts` time series format in R.

```{r}
singleObs <- getDataSet(dataLibrary, "var1_obs")
singleObs
plot(asXts(singleObs))
```

Some datasets are composites of several time series (e.g. multivariate series). Sub-identifiers can be specified to retrieve particular variables; this is particularly important for large datasets.

```{r}
stationIds <- GetEnsembleDatasetDataSubIdentifiers_R(dataLibrary, "var1_obs_collection")
print(stationIds)
multiObs <- getDataSet(dataLibrary, "var1_obs_collection")
multiObs
multiObs <- asXts(multiObs)
head(multiObs)
library(zoo)
plot.zoo(multiObs)
```

Data sets are meant to be discoverable. The data library can be queried for the main geometric characteristics of the data.

```{r}
GetEnsembleDatasetDataSummaries_R(dataLibrary)
```

Ensemble forecast time series (structurally, "time series of ensemble of time series") are supported as first class citizens by uchronia:

```{r}
fcasts <- getDataSet(dataLibrary, "var2_fcast_ens")
fcasts
# TODO: currently conversion ot xts is the default. Review:
firstFcast <- getItem(fcasts, 1)
head(firstFcast)
str(firstFcast)
plot.zoo(firstFcast, plot.type='single')
```
